---
title: "Intro to SLSIR package"
output:
    html_document:
        code_folding: show 
        section_numbers: true
        toc: true
        toc_depth: 4
        toc_float: true
---
```{r,include=FALSE}
library(devtools)
load_all(".")
```



# Introduction to the SLSIR package:

The simplest way to run a simulation is to use:

```{r,eval=F}
   simpleSimu=slsirSimu(pop=100,tstep=150)
```

The output of the simulation can be visualised by adding:

```{r simpleVisu,animation.hook="gifski",interval=0.05, aniopts="controls,loop",eval=FALSE}
   simpleSimu=slsirSimu(pop=100,tstep=150,visu=T)
```
In this visualisation, light blue squares represent agents conforming to social distancing, blue circle represent agents not conforming to social distancingcircle agents 

A more conveniant way to do a simulatoin, used in the paper, is to generate the population using `generatePopulation` as follow:
```{r}
    pop=generatePopulation(N=100,xsize=100,ysize=100,speed=1,recovery=1)
```
This will create a table with all information about the population:

```{r,echo=F}
    rmarkdown::paged_table(as.data.frame(pop))
```

Then the properties of the population can be adjusted 

```{r}
    pop[c(10:20),"speed"]=5 #agents 10 to 20 will go five time more quiclkly than all other agents
```

```{r}
   simpleSimu=slsirSimu(pop=pop,tstep=150,visu=T)
```

