---
title: "Intro to SLSIR package"
output:
    html_document:
        code_folding: show 
        section_numbers: true
        toc: true
        toc_depth: 4
        toc_float: true
---
```{r,include=FALSE}
library(devtools)
load_all(".")
```



# Introduction to the SLSIR package:

The simplest way to run a simulation is to use:

```{r,eval=F}
   simpleSimu=slsirSimu(pop=100,tstep=150)
```

The output of the simulation can be visualised by adding:

```{r simpleVisu,animation.hook="gifski",interval=0.05, aniopts="controls,loop",eval=FALSE}
   simpleSimu=slsirSimu(pop=100,tstep=150,visu=T)
```
In this visualisation, light blue squares represent agents conforming to social distancing, blue circle represent agents not conforming to social distancingcircle agents 

A more conveniant way to do a simulatoin, used in the paper, is to generate the population using `generatePopulation` as follow:
```{r}
    pop=generatePopulation(N=100,xsize=100,ysize=100,speed=1,recovery=1)
```
This will create a table with all information about the population:

```{r,echo=F}
    rmarkdown::paged_table(as.data.frame(pop))
```

Then the properties of the population can be adjusted 

```{r}
    pop[c(10:20),"speed"]=5 #agents 10 to 20 will go five time more quiclkly than all other agents
```

```{r}
   simpleSimu=slsirSimu(pop=pop,tstep=150,visu=T)
```

## More supplements

More analysis, those haven't been used in the paper and the code may not work.


```{r allmetricsall,out.width="30%"}

## distribution distances/metrics/4models
par(oma=c(0,2,0,0),mar=c(4,1,1,0))
for(v in c(1,4,7)){
    var=allscores[v]
        xlimits=range(sapply(allexpe,"[[",var))
        alld=lapply(allexpe,function(i,var)density(i[[var]]),var=var)
        ylimits=range(sapply(alld,"[[","y"))
        t=""
        if(v==1)t=expression(delta)
        if(v==4)t=expression(tau)
        if(v==7)t=expression(I[max])
        plot(1,1,ylim=ylimits,xlim=xlimits,type="n",main=t,yaxt="n",xlab=t,ylab="density")
        lapply(names(alld),function(i)lines(alld[[i]],col=modelcol[i],lwd=2))

}
legend("topleft",legend=modelsubnames,col=modelcol,lwd=3,lty=1)
mtext("density",2,0,outer=T)

for(var in allscores[c(7)+1]){
        xlimits=range(sapply(allexpe,"[[",var))
        alld=lapply(allexpe,function(i,var)density(i[[var]]),var=var)
        ylimits=range(sapply(alld,"[[","y"))
        plot(1,1,ylim=ylimits,xlim=xlimits,type="n",main=var,yaxt="n",xlab=var,ylab="density")
        lapply(names(alld),function(i)lines(alld[[i]],col=modelcol[i],lwd=3))

}
legend("topright",legend=modelsubnames,col=modelcol,lwd=3,lty=1)

for(var in allscores[c(1,4,7)+2]){
        xlimits=range(sapply(allexpe,"[[",var))
        alld=lapply(allexpe,function(i,var)density(i[[var]]),var=var)
        ylimits=range(sapply(alld,"[[","y"))
        plot(1,1,ylim=ylimits,xlim=xlimits,type="n",main=var,yaxt="n",xlab=var,ylab="density")
        lapply(names(alld),function(i)lines(alld[[i]],col=modelcol[i],lwd=3))

}
legend("topright",legend=modelsubnames,col=modelcol,lwd=3,lty=1)

#sapply(allexpe,function(i)quantile(i[[allscores[4]]],prob=.5)) 
```



Show the shape of sigmoid for the posteriors distributions

```{r visuSigShapeAllModel,eval=T,out.width="50%"}

for(mname in names(listallposterior)){
    x=seq(0,1,.01)
    par(mfrow=c(length(listallposterior[[mname]]),2),oma=c(3,3,2,0))
    par(mar=rep(.5,4))
    for(mod in names(listallposterior[[mname]])){
        best=listallposterior[[mname]][[mod]]
        plot(x,sig(x),type="n",ylim=c(0,1),xlim=c(0,1),xlab="% same age infected people", ylab="proba. to switch",main="",xaxt="n",yaxt="n")
        modsubname=paste0(strsplit(mname,"")[[1]][-(1:8)],collapse="")
        axis(2)
        mtext(modsubname,2.5,2,cex=.9)
        a=axis(1,outer=T)
        for(i in 1:nrow(best)) lines(x,sig(x,b=best$inf[i],a=best$sat[i]),ylim=c(0,1),xlim=c(0,1),col=adjustcolor(modelcol[mname],.1),lwd=2) 
        plot(x,sig(x),type="n",ylim=c(0,1),xlim=c(0,1),xlab="% same age infected people", ylab="proba. to switch",main="",xaxt="n",yaxt="n")
        for(i in 1:nrow(best)) lines(x,sig(x,b=best$inf_r[i],a=best$sat_r[i]),ylim=c(0,1),xlim=c(0,1),col=adjustcolor(modelcol[mname],.1),lwd=2) 
    }
    axis(1,outer=F)
    mtext(mname,3,1,outer=T)
}

```


```{r,out.width="45%"}

lapply(names(allexpe),function(mname){
       allresults=allexpe[[mname]]
       plot(allresults$time_max,allresults$max_infect,col=adjustcolor(color.gradient(allresults$distances,c(mygreen,"yellow", myred)),.2),main=mname,pch=20,xlab="Time Max",ylab="Max Infected")
       sset=sort(allresults$distances)
       cols=adjustcolor(color.gradient(sset,c(mygreen,"yellow", myred)),1)
       lsset=seq(1,length(sset),length.out=4)
       legend("topright",legend=sapply(round(sset[lsset],digit=2),function(d)as.expression(bquote(delta==.(d)))),col=cols[lsset],pch=20)
})


```


```{r plotAllPosteriorAllParam,eval=T}

modsubname=sapply(modelnames,function(mod)paste0(strsplit(mod,"")[[1]][-(1:8)],collapse=""))
parameters=colnames(allexpe$midCurve15Good)[1:6]
par(mfrow=c(3,length(parameters)),mar=c(1,2,2,1))
for(mbest in 1:length(listallposterior)){
    best=listallposterior[[mbest]]
    for(var in parameters){
        p=unlist(sapply(allexpe,"[[",var))
        xlimits=range(sapply(best,"[[",var),p)
        alld=lapply(best,function(i,var)density(i[[var]],from=xlimits[1],to=xlimits[2]),var=var)
        pd=density(p)
        if(var %in% c("sat_r","sat")){
            print(var)
            xlimits=c(-1,3)
            alld=lapply(best,function(i,var)density(log10(i[[var]]),from=xlimits[1],to=xlimits[2]),var=var)
            pd=density(log10(p),from=xlimits[1],to=xlimits[2])
        }
        ylimits=range(c(sapply(alld,"[[","y"),pd$y))
        plot(1,1,ylim=ylimits,xlim=xlimits,type="n",main=var,yaxt="n",xlab=var,ylab="density")
        lines(pd,lwd=3)
        lapply(names(alld),function(i)lines(alld[[i]],col=modelcol[mbest],lwd=3))
        if(var=="inf_r")legend("topleft",legend=modsubname,col=modelcol,lwd=3,lty=1)

    }
}



```



```{r sameButBetter,eval=T}

#### better separation use those::
parameters=colnames(allexpe$midCurve15Good)[1:6]
for(n in names(listallposterior)){
    sbest=listallposterior[[n]]
    #png(paste0("allposterior_metric_",n,".png"),width=1200,height=480,pointsize=15)
    par(mfrow=c(2,length(parameters)),mar=c(1,2,2,1),oma=c(3,3,0,0))
    sub=list(1:2,3:6)
    for( s in sub){
        best=sbest[s]
        for(var in parameters){
            p=unlist(sapply(allexpe,"[[",var))
            xlimits=range(sapply(best,"[[",var),p)
            alld=lapply(best,function(i,var)density(i[[var]],from=xlimits[1],to=xlimits[2]),var=var)
            pd=density(p)
            if(var %in% c("sat_r","sat")){
                print(var)
                xlimits=c(-1,3)
                alld=lapply(best,function(i,var)density(log10(i[[var]]),from=xlimits[1],to=xlimits[2]),var=var)
                pd=density(log10(p),from=xlimits[1],to=xlimits[2])
            }
            ylimits=range(c(sapply(alld,"[[","y"),pd$y))
            plot(1,1,ylim=ylimits,xlim=xlimits,type="n",main=var,yaxt="n",xlab=var,ylab="density")
            lines(pd,lwd=3)
            lapply(names(alld),function(i)lines(alld[[i]],col=modelcol[s],lwd=3))
            if(var=="sl_rad")legend("bottom",legend=modelsubnames[s],col=modelcol[s],lwd=3,lty=1)
        }

        }
        mtext("t0 : 15-100% A",2,1,0.3,outer=T) 
        mtext("t0 : 0% NA",2,1,0.7,outer=T) 
}
```


```{r,eval=F}

for(n in names(listallposterior)){
    sbest=listallposterior[[n]]
    sbest=sbest[-5]


    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=sbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        tryCatch({hdr.boxplot.2d(best$inf_r,log10(best$sat_r),prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],1),xlim=c(0,1),ylim=c(-1,3),xlab="revert inf. point",ylab="revert steepness (log10)")},error=function(e){print(e);print(mod)})
    }
    mtext("inf_r",1,2,outer=T)
    mtext("sat_r",2,2,outer=T)

    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)

    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)
    
    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        tryCatch({hdr.boxplot.2d(best$inf,log10(best$sat),prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(0,1),ylim=c(-1,3),xlab="inflexion point",ylab="steepness (log10)")},error=function(e){print(e);print(mod)})
    }
    mtext("inf",1,2,outer=T)
    mtext("sat",2,2,outer=T)
                                     
    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)

    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)
                                 
    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        hdr.boxplot.2d(best$inf,best$pind,prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(0,1),ylim=c(0,1),xlab="inflexion point",ylab="individual learning")
    }
    mtext("inf",1,2,outer=T)
    mtext("pind",2,2,outer=T)

    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)

    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)


    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        hdr.boxplot.2d(log10(best$sat),best$pind,prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(-1,3),ylim=c(0,1),xlab="steepness (log10)",ylab="individual learning")
    }
    mtext("sat",1,2,outer=T)
    mtext("pind",2,2,outer=T)

    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)
                                
    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)
                                 

    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        hdr.boxplot.2d(best$sl_rad,best$pind,prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(1,100),ylim=c(0,1),xlab="radius social learning",ylab="individual learning")
    }
    mtext("sl_rad",1,2,outer=T)
    mtext("pind",2,2,outer=T)
    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)
    
    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)

    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        hdr.boxplot.2d(best$sl_rad,best$inf,prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(1,100),ylim=c(0,1),xlab="radius social learning",ylab="infection points")
    }
    mtext("sl_rad",1,2,outer=T)
    mtext("inf",2,2,outer=T)

    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)
                                
    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)
                                 
par(xpd=NA)
    par(mar=c(1,1,1,1),oma=c(3,3,3,3),xpd=T)
    par(mfrow=c(3,2))
    for(mod in names(sbest)){
        best=listallposterior$allbest[[mod]]
        if(mod=="burnin100BestSLS")plot.new()
        hdr.boxplot.2d(best$sl_rad,log10(best$sat),prob=seq(20,100,10),shadecols=adjustcolor(modelcol[mod],.9),xlim=c(1,100),ylim=c(-1,3),xlab="sl_rad",ylab="steepness (log10)")
    }
    mtext("sl_rad",1,2,outer=T)
    mtext("sat",2,2,outer=T)

    mtext("random SL",3,1,.3,outer=T)
    mtext("best SL",3,1,.7,outer=T)
                                
    mtext("wait100A",4,1,.15,outer=T)
    mtext("15%A",4,1,.5,outer=T)
    mtext("0%AD",4,1,,.85,outer=T)
                                 
}

```


```{r,eval=F}


par(mfrow=c(2,4),oma=c(0,4,0,0))
 
plot(density(log10(listallposterior$allbest$midCurveAllBad$sat),from=-1,to=3),ylim=c(0,.45),main="sat",xlab="sat")
lines(density(log10(listallposterior$allbest_max_infect150$midCurveAllBad$sat)),col="red")
lines(density(log10(allexpe$midCurveAllBad$sat)),col="grey")
legend("topright",legend=c("final time","150ts", "prior"),lwd=1,col=c(1,2,"grey"))
mtext("normal model",2,5)

plot(density(listallposterior$allbest$midCurveAllBad$inf,from=0,to=1),ylim=c(0,2),main="inf",xlab="inf")
lines(density(listallposterior$allbest_max_infect150$midCurveAllBad$inf,from=0,to=1),col="red")
lines(density(allexpe$midCurveAllBad$inf),col="grey")

plot(density(log10(listallposterior$allbest$midCurveAllBad$sat_r),from=-1,to=3),ylim=c(0,.7),main="sat_r",xlab="sat_r")
lines(density(log10(listallposterior$allbest_max_infect150$midCurveAllBad$sat_r)),col="red")
lines(density(log10(allexpe$midCurveAllBad$sat_r)),col="grey")

plot(density(listallposterior$allbest$midCurveAllBad$inf_r,from=0,to=1),ylim=c(0,6),main="inf_r",xlab="inf_r")
lines(density(listallposterior$allbest_max_infect150$midCurveAllBad$inf_r,from=0,to=1),col="red")
lines(density(allexpe$midCurveAllBad$inf_r),col="grey")

plot(density(log10(listallposterior$allbest$midCurveAllBad$sat),from=-1,to=3),ylim=c(0,.45),main="sat",xlab="sat")
lines(density(log10(listallposterior$allbest_max_infect150$midCurveAllBad$sat)),col="red")
lines(density(log10(allexpe$midCurveAllBad$sat)),col="grey")
legend("topright",legend=c("final time","150ts", "prior"),lwd=1,col=c(1,2,"grey"))
mtext("waiting 100ts ",2,5)

plot(density(listallposterior$allbest$midCurveAllBad$inf,from=0,to=1),ylim=c(0,2),main="inf",xlab="inf")
lines(density(listallposterior$allbest_max_infect150$midCurveAllBad$inf,from=0,to=1),col="red")
lines(density(allexpe$midCurveAllBad$inf),col="grey")

plot(density(log10(listallposterior$allbest$midCurveAllBad$sat_r),from=-1,to=3),ylim=c(0,.7),main="sat_r",xlab="sat_r")
lines(density(log10(listallposterior$allbest_max_infect150$midCurveAllBad$sat_r)),col="red")
lines(density(log10(allexpe$midCurveAllBad$sat_r)),col="grey")

plot(density(listallposterior$allbest$midCurveAllBad$inf_r,from=0,to=1),ylim=c(0,6),main="inf_r",xlab="inf_r")
lines(density(listallposterior$allbest_max_infect150$midCurveAllBad$inf_r,from=0,to=1),col="red")
lines(density(allexpe$midCurveAllBad$inf_r),col="grey")



par(mfrow=c(1,2))
plot(1,1,ylim=c(0,500),xlim=c(0,500),type="n",main="#infected")
 for(f in list.files("testingSimHigSL/" ,pattern="allG_*",full.names=T)){ 
     load(f)
     lines(simu$timeseries[,2],col="green")
}
 for(f in list.files("testingSimHigSL/" ,pattern="allB_*",full.names=T)){ 
     load(f)
     lines(simu$timeseries[,2],col="red")
}
plot(1,1,ylim=c(0,500),xlim=c(0,500),type="n",main="#Adherent")
 for(f in list.files("testingSimHigSL/" ,pattern="allG_*",full.names=T)){ 
     load(f)
     lines(simu$timeseries[,5],col="green")
}
 for(f in list.files("testingSimHigSL/" ,pattern="allB_*",full.names=T)){ 
     load(f)
     lines(simu$timeseries[,5],col="red")
}

```

