---
title: "Vignette to reproduce the graph in 'How Social Learning Shapes the Efficacy of Preventative Health Behaviors in an Outbreak' "
output:
    html_document:
        code_folding: show
        section_numbers: true
        toc: true
        toc_depth: 4
        toc_float: true
---
```{r initialisation,echo=F,message=FALSE,warning=FALSE}
knitr::opts_chunk$set(echo = TRUE,message=FALSE,warning=FALSE,cache=TRUE,fig.show="hold",result.show="hide")

library(devtools)
load_all("..")
color_class=rev(brewer.pal(5,"PuBu"))
colorbest=color_class[1]
myred=rgb(r=213,g=94,b=0,maxColorValue=255)
myred="red"
mygreen=rgb(r=0,g=158,b=115,maxColorValue=255)
mygreen=colorbest
```

# Main Paper
## Fig2
A sigmoid function `sig`:

$$ p \sim \frac{1}{1+e^{-\kappa\times(x-\nu)}} $$

```{r, illusig,fig.cap="illustration of switch parameters",out.width="50%"}
par(mar=c(4,4,1,1))
x=seq(0,1,.01)
inp=seq(0,1,.05)
clrs=colorRampPalette(c("purple4","yellow"))(length(inp))
plot(x,sig(x),type="n",ylim=c(0,1),xlim=c(0,1),xlab="% infected",ylab=expression(P[switch]),main="" )
for(i in 1:length(inp)) lines(x,sig(x,b=inp[i],a=4),ylim=c(0,1),xlim=c(0,1),col=clrs[i],lwd=2)
leg=seq(1,length(inp),length.out=5)
legend("bottomright",legend=rev(sapply(inp[leg],function(d)as.expression(bquote(.(d))))),title=expression(nu),col=rev(clrs[leg]),lwd=2,cex=.8,bg="white")

tstp=25
stp=rev(seq(-3,3,length.out=tstp))
clrs=colorRampPalette(c("purple4","yellow"))(tstp)
plot(x,sig(x),type="n",ylim=c(0,1),xlim=c(0,1),xlab="% infected",ylab=expression(P[switch]),main="" )
for(i in rev(1:length(stp))) lines(x,sig(x,a=10^stp[i]),ylim=c(0,1),xlim=c(0,1),col=clrs[i],lwd=2)
leg=seq(1,tstp,length.out=5)
legend("bottomright",legend=sapply(round(stp[leg]),function(d)as.expression(bquote(.(10^d)))),col=clrs[leg],lwd=2,title=expression(kappa),cex=.8,bg="white")

```





## Fig3.tiff

A figure to illustrate different way to flatten the curve. We ran several simulationi in two different setup to show the differences between two situation: one when there is no social distancing, one in which there is.

### Static simulations
The simulations have been run using:

```{r,simulateSimple,eval=F}

library(parallel)
xsize=ysize=100
pop=generatePopulation(N=500,xsize=xsize,ysize=ysize,recovery=c(8,14)*25,speed=c(1,.2),behavior=rep(B,500))
cl <- makeForkCluster(18,outfile="")
neutralNSD=parSapply(cl,1:500,function(i){
                     print(i);
                     simu=slsirSimu(tstep=1500,p=c(1,1),di=2,i0=1,xsize=xsize,ysize=ysize,
                                    pop=pop,
                                    inf=9,
                                    sat=1000,
                                    p_i=1,
                                    strategy="best",
                                    ts=T,ap=F,visu=F
                                    )$timeseries[,2]

})
save(file="neutralNSD.bin",neutralNSD)

pop[,"behavior"]=G
neutralSD=parSapply(cl,1:500,function(i){
                    print(i);
                    simu=slsirSimu(tstep=1500,p=c(.1,.1),di=2,i0=1,xsize=xsize,ysize=ysize,
                                   pop=pop,
                                   inf=9,
                                   sat=1000,
                                   p_i=1,
                                   strategy="best",
                                   ts=T,ap=F,visu=F
                                   )$timeseries[,2]

})
save(file="neutralSD.bin",neutralSD)


neutralSD2=parSapply(cl,1:500,function(i){
                     print(i);
                     simu=slsirSimu(tstep=1500,p=c(.1,.1),di=2,i0=1,xsize=xsize,ysize=ysize,
                                    pop=pop,
                                    inf=9,
                                    sat=1000,
                                    p_i=1,
                                    strategy="random",
                                    ts=T,ap=F,visu=F
                                    )$timeseries[,2]

})
save(file="neutralSD2.bin",neutralSD2)
stopCluster(cl)
```


### plot figure
```{r}
par(mar=c(2,2,2,2))
plot(1,1,type="n",ylim=c(0,500),xlim=c(1,1500),ylab="",xlab="",xaxt="n",yaxt="n")
legend("topright",legend=c("No social distancing","Social distancing"),fill=c(myred,mygreen),cex=.95)
mtext("time",1,1)
mtext("number of infected people",2,1)

load("../data/neutralSD.bin")
load("../data/neutralNSD.bin")
load("../data/neutralSD2.bin")
#we use precomputed data to compute a mean curve, those data have been generated using the scripts in "exec/graphPaper.R"

meanNSD=apply(neutralNSD,1,mean)
meanSD=apply(neutralSD,1,mean)

polygon(0:1500,meanSD,col=adjustcolor(mygreen,.5),border=NA)
polygon(0:1500,meanNSD,col=adjustcolor(myred,.5),border=NA)
lines(meanSD,col=adjustcolor(mygreen,.9),lwd=2)
lines(meanNSD,col=adjustcolor(myred,.9),lwd=2)

abline(h=max(meanNSD),lty=2,col=myred)
abline(v=which.max(meanNSD),lty=2,col=myred)
abline(h=max(meanSD),lty=2,col=mygreen)
abline(v=which.max(meanSD),lty=2,col=mygreen)

text(bquote(paste("max infected (",I[max],") no SD")),x=1500,y=max(meanNSD)+10,pos=2,cex=.8)
mtext(bquote(paste("time max (",tau,") no SD")),at=which.max(meanNSD),adj=1,cex=.8)
text(bquote(paste("max infected (",I[max],") SD")),x=1500,y=max(meanSD)+10,pos=2,cex=.8)
mtext(bquote(paste("time max (",tau,") SD")),at=which.max(meanSD),adj=0,cex=.8)

abline(v=which.max(meanNSD),lty=2,col=myred)
abline(h=max(meanSD),lty=2,col=mygreen)
abline(v=which.max(meanSD),lty=2,col=mygreen)
```




## Fig4.tiff

In this figure we present the overall results of the main simulations, with some some analysis of $\delta$, the score of each simulation.

### Run all simulations

To runn all simulation one need the script in `exec`
```{r,runallsimu}



```

Those generate a lot of data, we then amde available the result of our simulation here:

you cann download

```bash
wget  httpe://adsdas.ads
```




To get the results of the simulation then just:
```{r,getallresults}
name='../data/midCurveAllBadBestSLS/'
aa=lapply(unlist(lapply(list.dirs(name),list.files,pattern="allresults.bin",full.names=T)),function(f){load(f);return(allresults)})
allresults=do.call("rbind",aa)
#allresults=allresults[allresults$inf <.02 & allresults$sat >10,]
allresults=allresults[-which(allresults$max_infect <4),] #we remove the results where no outbreak happend
allresults$distances=(1-bdistance(allresults$time_max) + bdistance(allresults$max_infect))/2
```

For this Figure we also want to compare how simulations with different score relates to the case with no social learning. For that we re-run simulations. These simulations take time so we give the results in `data/`


### Re-run best/worst results

```{r,repeatworstebest,eval=F}

library(parallel)
cl <- makeForkCluster(16,outfile="")

best=allresults[order(allresults$distances),][1:1000,]
worst=allresults[order(allresults$distances,decreasing=T),][1:1000,]

repetBest=parSapply(cl,1:500,function(i){
                    j=sample(nrow(best),1);print(paste(i,j));
                    simu=slsirSimu(500,1500,p=c(1,.1),di=2,i0=1,recovery=c(8,14)*25,speed=c(1,.2),xsize=xsize,ysize=ysize,
                                inf=best$inf[j],
                                sat=best$sat[j],
                                inf_r=best$inf_r[j],
                                sat_r=best$sat_r[j],
                                p_i=best$pind[j],
                                sl_rad=best$sl_rad[j],
                                strategy="best",
                                ts=T,ap=F,visu=F
                                )$timeseries[,2]
})
save(file="repetBest.bin",repetBest)

repetWorst=parSapply(cl,1:500,function(i){
                    j=sample(nrow(worst),1);print(paste(i,j));
                    simu=slsirSimu(500,1500,p=c(1,.1),di=2,i0=1,recovery=c(8,14)*25,speed=c(1,.2),xsize=xsize,ysize=ysize,
                                inf=worst$inf[j],
                                sat=worst$sat[j],
                                inf_r=worst$inf_r[j],
                                sat_r=worst$sat_r[j],
                                p_i=worst$pind[j],
                                sl_rad=worst$sl_rad[j],
                                strategy="best",
                                ts=T,ap=F,visu=F
                                )$timeseries[,2]
})
save(file="repetWorst.bin",repetWorst)

stopCluster(cl)
```

```{r,getallresultsShort}
load("../data/repetBest.bin") 
load("../data/repetWorst.bin") 
meanWorst=apply(repetWorst,1,mean) #
meanBest=apply(repetBest,1,mean) #
```

### generate Figure

We can now plot the graph of the paper

```{r, fig.cap="Fig 4: mean trajectories and scores for simulations", out.width="50%"}
### left panel
par(mar=c(4,4,2,2))
plot(1,1,type="n",ylim=c(0,500),xlim=c(1,1500),ylab="",xlab="",xaxt="n",yaxt="n")
abline(v=150,lwd=2,col="gray")
par(xpd=NA)
text(150,-20,"t=150",col="1",pos=1)
par(xpd=F)
legend("topright",legend=c("No Learning (all NA)","No Learning (all A)","Worst Simulations","Best Simulations"),col=c(myred,mygreen),lty=c(1,1,2,2),lwd=2,cex=.95)
axis(1)
axis(2)
mtext("time",1,3)
mtext("number of infected people",2,3)


lines(meanSD,col=adjustcolor(mygreen,.9),lwd=2)
lines(meanNSD,col=adjustcolor(myred,.9),lwd=2)
lines(meanBest,col=adjustcolor(mygreen,.9),lwd=2,lty=2)
lines(meanWorst,col=adjustcolor(myred,.9),lwd=2,lty=2)

### right panel
subresults=allresults[sample(nrow(allresults),20000),]
rank=rank(subresults$distances)
orderscol=rank
color_class=rev(brewer.pal(5,"PuBu"))
colorbest=color_class[1]
orderscol=rep(adjustcolor(color_class[5],.4),length(orderscol))
nvl=c(1000,2500,5000,10000)
for(i in (length(nvl):1)) orderscol[rank<=nvl[i]]=adjustcolor(color_class[i],.4)
#plot(subresults$time_max,subresults$max_infect,bg=orderscol,main=expression(I[max]*" wrt "*tau),pch=21,xlab=expression(tau),ylab=expression(I[max]),lwd=.1)
plot(subresults$time_max,subresults$max_infect,bg=orderscol,main="",pch=21,xlab=expression(tau),ylab=expression(I[max]),lwd=.1)
legend("topright",legend=c(paste("<",nvl),"all"),pt.bg=color_class,pch=21,col=adjustcolor(1,.5),pt.lwd=.1,title="Rank")
```

## Fig5

For this figure we need the posterior distribution of our model given by the distance to the data as measured by our $\delta$

###  Get the posterior

```{r}
n=1000
posterior=list(
               best=allresults[order(allresults$distances),][1:n,],
               worst=allresults[order(allresults$distances,decreasing=T),][1:n,],
               time_max=allresults[order(allresults$time_max,decreasing=T),][1:n,],
               time_max150=allresults[order(allresults$time_max150,decreasing=T),][1:n,],
               time_max250=allresults[order(allresults$time_max250,decreasing=T),][1:n,],
               wtime_max150=allresults[order(allresults$time_max150,decreasing=F),][1:n,],
               wtime_max250=allresults[order(allresults$time_max250,decreasing=F),][1:n,],
               max_infect=allresults[order(allresults$max_infect,decreasing=F),][1:n,],
               max_infect150=allresults[order(allresults$max_infect150,decreasing=F),][1:n,],
               max_infect250=allresults[order(allresults$max_infect250,decreasing=F),][1:n,],
               wmax_infect150=allresults[order(allresults$max_infect150,decreasing=T),][1:n,],
               wmax_infect250=allresults[order(allresults$max_infect250,decreasing=T),][1:n,]
               )

```




```{r,2dHDRplots,out.width="50%",fig.cap="Top row: distriution of parameter that gives us the best results when simulation reach 150 steps, bottom row: when the simulation reaches 1500. Left column: parameters to swtich from NA to A, right column to switch from NA to A",message=F,warning=F}
library(hdrcde)

duocolrs=adjustcolor(c(myred,colorbest),.8)
currange=range=list(dim1=c(0,1),dim2=c(-1,3))
dimlab=list(dim1=expression(nu),dim2=expression(kappa))

### Cmpound marginal with 2d  learning
expnames=c(distribA="Worst 150",distribB="Best 150")
marginAndJoin(
              distribA=list(dim1=posterior$wmax_infect150$inf,dim2=posterior$wmax_infect150$sat),
              distribB=list(dim1=posterior$max_infect150$inf,dim2=posterior$max_infect150$sat),
              dimlab=list(dim1=expression(nu),dim2=expression(kappa)),
              expnames=expnames, range=currange,cols=duocolrs,log="y",
              main=""
              )

expnames=c(distribA="Worst 150",distribB="Best 150")
marginAndJoin(
              distribA=list(dim1=posterior$wmax_infect150$inf_r,dim2=posterior$wmax_infect150$sat_r),
              distribB=list(dim1=posterior$max_infect150$inf_r,dim2=posterior$max_infect150$sat_r),
              dimlab=list(dim1=expression(nu[r]),dim2=expression(kappa[r])),
              expnames=expnames, range=currange,cols=duocolrs,log="y",
              main=""
              )

expnames=c(distribA="Worst",distribB="Best")
marginAndJoin(
              distribA=list(dim1=posterior$worst$inf,dim2=posterior$worst$sat),
              distribB=list(dim1=posterior$best$inf,dim2=posterior$best$sat),
              dimlab=list(dim1=expression(nu),dim2=expression(kappa)),
              expnames=expnames, range=currange,cols=duocolrs,log="y",
              main=""
              )


expnames=c(distribA="Worst",distribB="Best")
marginAndJoin(
              distribA=list(dim1=posterior$worst$inf_r,dim2=posterior$worst$sat_r),
              distribB=list(dim1=posterior$best$inf_r,dim2=posterior$best$sat_r),
              dimlab=list(dim1=expression(nu[r]),dim2=expression(kappa[r])),
              expnames=expnames, range=currange,cols=duocolrs,log="y",
              main=""
              )


```


# Supplementary Material




